RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-09-05 main.tex
:pencil: Update contributions

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr}; 4) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.

>>>>

		\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
		The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
		Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with ambient devices, but the advantages are
		1) RIScatter nodes can be built over universal load-switching scatterers instead of composite metamaterial;
		2) backscatter modulation and passive beamforming are unified by input distribution instead of advanced hardware architecture;
		3) optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients;
		4) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional equiprobable line coding in \gls{bc}/\gls{sr};
		5) the potentially dispersed characteristics of RIScatter nodes (and legacy users) avoids the development optimization and allows uniformly good performance for both links.
